\title{sitandr.github.io/typst-examples-book/book/about}

\section{\texorpdfstring{\hyperref[typst-examples-book]{Typst Examples
Book}}{Typst Examples Book}}\label{typst-examples-book}

This book provides an extended \emph{tutorial} and lots of
\href{https://github.com/typst/typst}{Typst} snippets that can help you
to write better Typst code.

This is an unofficial book. Some snippets \& suggestions here may be
outdated or useless (please let me know if you find some).

However, \emph{all of them should compile on last version of Typst
\textsuperscript{\hyperref[1]{1}}} .

\textbf{CAUTION:} the book is (probably forever) a \textbf{WIP} , so
don\textquotesingle t rely on it.

If you like it, consider
\href{https://github.com/sitandr/typst-examples-book}{giving a star on
GitHub} !

This will help me to stay motivated and continue working on this book.

\subsection{\texorpdfstring{\hyperref[navigation]{Navigation}}{Navigation}}\label{navigation}

The book consists of several chapters, each with its own goal:

\begin{enumerate}
\tightlist
\item
  \href{./basics/index.html}{Typst Basics}
\item
  \href{./snippets/index.html}{Typst Snippets}
\item
  \href{./packages/index.html}{Typst Packages}
\item
  \href{./typstonomicon/index.html}{Typstonomicon}
\end{enumerate}

\subsection{\texorpdfstring{\hyperref[contributions]{Contributions}}{Contributions}}\label{contributions}

Any contributions are very welcome! If you have a good code snippet that
you want to share, feel free to submit an issue with snippet or make a
PR in the
\href{https://github.com/sitandr/typst-examples-book}{repository} .

I will especially appreciate submissions of active community members and
compiler contributors!

However, I will also really appreciate feedback from beginners to make
the book as comprehensible as possible!

\subsection{\texorpdfstring{\hyperref[acknowledgements]{Acknowledgements}}{Acknowledgements}}\label{acknowledgements}

Thanks to everyone in the community who published their code snippets!

If someone doesn\textquotesingle t like their code and/or name being
published, please contact me.

\phantomsection\label{1}
\textsuperscript{1}

When a new version launches, it may take some time to update the book,
feel free to tag me to speed up the process.
